ZCB Pricing

### 2018-07-27 ZCB Pricing .Rmd
ffff

@@

Control_Variates_estimate= function(alpha, beta, sigma,t,T,r0,n,s){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}

@@

CR <- NULL
AV <- NULL
MM <- NULL

@@

plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
lines(xvec,AV, col ="black", lty =1.5)
lines(xvec,MM, col ="yellow", lty =1.5)
```

>>>>

Crude_Monte_Carlo()
bond_price()
```

@@

Control_Variates_estimate= function(alpha =0.08,beta=0.8,sigma=0.005,t=0,T=1,r0 = 0.08,n=1000,s=100){
  Crude_Monte_Carlo(alpha,beta,sigma,T,r0,n,s)[1]- CIR_MC(alpha,beta,sigma,T,r0,n,s)[1]+bond_price_CIR(alpha,beta,sigma,t,T,r0)
}

V=seq(0.01,0.05,0.01)
J=NULL
K=NULL
for ( i in 1:length(V)){
  J[i]=Control_Variates_estimate(r0=V[i])
  K[i]=bond_price(r=V[i])
}
P=(J-K)^2
P
```

```{r}
# Comparisons of different methods
#################################################################################
# Stability of results
#################################################################################

# We do this by checking the variance amongst the results when simulated many times.

r_vec=seq(-0.4,0.5,0.005)
CR=NULL
N=NULL
for (i in 1:length(r_vec)){
  CR[i]=Crude_Monte_Carlo(r0=r_vec[i])
  if(CR[i])
}

Var=var(CR)
Var
CR
Crude_Monte_Carlo(r0=-0.4)
```

@@

CR <- NULL
AV <- NULL
MM <- NULL
CO <- NULL

@@

for (t in 1: length(xvec)){
  CO[t] <- Control_Variates_estimate(r0 = xvec[t], T =5)

plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
lines(xvec,AV, col ="black", lty =1.5)
lines(xvec,MM, col ="yellow", lty =1.5)
lines(xvec,MM, col ="green", lty =1.5)
```
